\subsection{Excercise UMEGeneralConcepts}
\label{sec:ume_general_concepts}
%//TODO: Kurze Einleitung
\subsubsection*{Architectural Style}
The Unified Microservice Engineering approach aligns with the microservices architectural style.
This involves breaking down an application into smaller, independent services that can be developed, deployed, and scaled separately.
The services communicate with each other through APIs and are usually organized around business capabilities.
These services aim to enhance flexibility, scalability, and maintainability.

Predecessors of the microservices architectural style are the service-oriented architecture (SOA) and the distributed systems architectural style which will be further explained in the following.

\paragraph*{Service Oriented Architecture}
SOA shares some similarities with the microservices architectural style.
The focus is on organizing services around business capabilities and developing them independently.
This aims to achieve reusability and interoperability.

Yet, microservices tend to be generally smaller, more fine-grained, decoupled and are usually lightweight.

\paragraph*{Distributed Systems}
Distributed systems represent a collection of independent computers, appearing to the users of the system as a single coherent system.
These systems handle tasks across a network, each node having its local memory and set of responsibilities.

Microservices share a similar idea: Splitting an application into smaller, more independent services communicating with each other.
Each microservice manages its functionalities and data to provide the overall functionality of the application.

\subsubsection*{Domain Modelling}
A domain model describes selected aspects of a domain in a conceptual model, yet the model should not separate the concept from the implementation.
This model can be used to better understand the domain and to communicate with stakeholders.

The domain model is located in the domain logic layer of the layered architecture.
Therefore each microservice implements its domain model.

Using a layered software architecture, the business logic layer is separated into application logic and domain logic.
The application logic layer contains the application-specific logic while the domain logic layer contains the domain-specific logic.
This domain-specific logic is derived from the domain model, enabling the domain knowledge to be encapsulated in the domain logic layer.
The application logic layer is derived from the analysis of the application requirements, for instance, use cases.

Therefore the domain logic layer is the part of the software architecture that is shaped the most by domain modeling.

\subsubsection*{Modelling of the Architecture}
To model the architecture of a microservice-based application, UME uses the Unified Modeling Language (UML).
To create the according diagrams, the UMLet tool is used.

Two modeling views can be distinguished: the tactical and the strategic view.

The strategic modeling provides an overview of the domain model.
The result is the so-called context map.
It provides the link to the microservice architecture.
The context map consists of subdomains and their bounded contexts.
A bounded context can be seen as a microservice candidate.

Tactical modeling takes a closer look at the entities and their relationships.
Each bounded context entity models the static relations of the domain entity.

\subsection{Excercise APIStyles}
\label{sec:api_styles}
%//TODO: Kurze Einleitung
\subsubsection*{REST and gRPC}
Representational State Transfer (REST) and 

\subsubsection*{REST Properties}


\subsubsection*{gRPC Components}


\subsubsection*{Use of REST and gRPC in UME}

\subsection{Excercise ArchitectureCarRentalAppV1.0}
\label{sec:architecture_car_rental_app_v1_0}
%//TODO: Kurze Einleitung