\chapter{M2Go Part 2: Golang}
\label{cha:golang}
%//TODO am Schluss nochmal drübergehen und checken, dass kein "we" oder "us" benutzt wird
This section introduces the Golang programming language.
It is a compiled, statically typed language developed by Google, commonly used for network and web applications.
Its performance and simplicity make it a good choice for microservices, APIs and other network applications.

The first section is about setting up the Golang environment and cloning the gitlab repository.
\autoref{sec:basic_go_program} will introduce the basic syntax of Golang by implementing a simple hello world program.
\autoref{sec:go_program_car_rental} will manifest the basic Golang knowledge by analysing the structure and requirements of the CarRental program.
Finally, \autoref{sec:advanced_go_program_car_rental_cli} will introduce advanced Golang features by implementing a command line interface for the CarRental program.

%==============================================================================

\section{M2Go Environment Installation}
\label{sec:m2go_env_installation}
This section will provide guidance on how to install the Golang environment and how to clone the gitlab repository.

\input{chapters/2_golang_tasks/2.1_excercise_install_go_env.tex}
\input{chapters/2_golang_tasks/2.2_cm_gitlab_usage.tex}

%==============================================================================

\section{Basic Go Program HelloWorld}
\label{sec:basic_go_program}
This section implements a simple hello world program, introdcing the basic syntax of Golang.

\input{chapters/2_golang_tasks/2.3_basic_hello_world_program.tex}

%==============================================================================

\section{Go Program CarRental}
\label{sec:go_program_car_rental}
This section introduces fundamental programming concepts in Golang.
First, the requirements analysis of the CarRental program is conducted, by reviewing an informal story in section \ref{sec:exercise_use_case_diagram_car_rental}.
The following design-phase in section \ref{cha:design_of_data_and_functionality} spepcifies data structures and the functionality of the use case.
The last section introduces concepts of implementing and testing the design artifacts.

\input{chapters/2_golang_tasks/3.1_requirements_analysis.tex}
\input{chapters/2_golang_tasks/3.2_design_of_data_and_functionality.tex}
\input{chapters/2_golang_tasks/3.3_implementation_and_test.tex}

%==============================================================================

\section{Advanced Go Program CarRentalCLI}
\label{sec:advanced_go_program_car_rental_cli}
This section introduces advanced programming concepts in Golang.

The actor needs to input data into the CarRental program to interact with it.
Therefore, CarRentalCLI implements a simple command line interface (CLI) for the CarRental program.

The following tasks will introduce the application by analysing the software and micro architecture.
After understanding the program, commands and mappers will be added.
After that, the program will be tested according to a list of OCL constraints.

In the end of this section, further use cases and functionality will be implemented as part of a challenge.

\input{chapters/2_golang_tasks/4.0_advanced_go_program.tex}
\input{chapters/2_golang_tasks/4.3_tests.tex}
\input{chapters/2_golang_tasks/4.4_challenge.tex}

%==============================================================================