\section{API Design of DM-Car}
\label{sec:api_design}
% Wichtig: Die Ergebnisse sollten klar und konkret beschrieben werden, aber auch nicht allzu überschwänglich
\subsection{Excercise DomainEntityCarV1.0}
\label{subsec:domain_entity_car_v1.0}
\subsubsection*{DDD Pattern}
Domain-Driven-Design includes a set of patterns solving common problems elegantly.
Besides the already-known layered architecture pattern, the entity pattern is part of the DDD-core patterns.
An entity is described to be an object, that is not defined by its attributes, but by a thread of continuity and its identity.

A car is a good example of an entity because it is not defined by its attributes but by its identity.
In our case, the identity is the VIN (Vehicle Identification Number), the brand and the model.
The attributes can be the color, the engine, etc.
Even if the attributes change, the car is still the same entity due to its unique and therefore constant identity.

Therefore the entity pattern is a good choice for the car.

\subsubsection*{Terms Used}
This section describes the terms used in the \texttt{domain\_entity\_car\_v1.0} file as it is shown in \texttt{gu\_terms\_used}.
\paragraph*{domain entity:}
This shows, that this entity is part of the domain.
\paragraph*{vin:}
The VIN (Vehicle Identification Number) is a unique identifier for a car.
It therefore is part of the car's identity.
\paragraph*{brand:}
This is the brand of the car.
It also is part of the car's identity.
\paragraph*{model:}
This is the model of the car.
It is part of the car's identity.

\subsubsection*{Example Data}
This task adds the example data to the table of example data.
The example data is given in the task sheet.
The results are shown in \autoref{tab:example_data_domain_entity_car_v1.0}.
\begin{table}
    \centering
    \caption{Example Data of DomainEntityCarV1.0}
    \label{tab:example_data_domain_entity_car_v1.0}
    \begin{tabular}{|p{5cm}|p{2cm}|p{2cm}|}
        \hline
        vin & brand & model \\
        \hline
        JH4DB1561NS000565 & VW & ID2 \\
        JN8AZ2NC5B9300256 & VW & ID3 \\
        2FDKF38G3KCA42390 & Ford & Mustang \\
        1GBJK39DX6E165432 & Tesla & Model S \\
        JH4DB1550MS003978 & Audi & A3 \\
        \hline
    \end{tabular}
\end{table}

\subsection{Excercise APIDiagramDMCarV1.0}
\label{subsec:api_diagram_dm_car_v1.0}


\subsection{Excercise PrepareLocalWorkingFolder}
\label{subsec:prepare_local_working_folder}