\subsection{Excercise MicroArchDMCar}
%//TODO introduction
\subsubsection*{Parts of a Micro Architecture}
The microarchitecture specifies the internal code structure of the microservice.
It plays a major role in the further development and maintenance process whether on the chosen complexity.
The basic structure of a microservice's microarchitecture is divided into three separate parts: the Microservice Requester, the Microservice API, and the Persistency Interface.
Each of these parts is described in more detail in the following.

\paragraph*{Microservice Requester:}
The Microservice Requester is the software unit sending requests to the microservice and receiving the microservice's responses.
This can be the front end or another microservice.

\paragraph*{Microservice API:}
Each microservice implements and provides an API.
It is defined by the microservice's specification and is usually based on REST or gRPC depending on the microservice's requirements.
The API contains the Domain or Application logic, based on the type of microservice.
It implements the according operations and logic.
The logic is structured according to the given operations.

\paragraph*{Persistency Interface:}
This part provides the data elements like entities or value objects.
These elements can be accessed by the operations.
This enables decoupling of the interface to the database by which the data elements are stored.

\subsubsection*{Parts of the DM-CarV1.0 Micro Architecture}

\subsubsection*{Micro Architecture in VS Code}

\subsection{Excercise LogicPartDMCar}
\subsubsection*{Content of the Logic Folder}
\subsubsection*{Repository Interface}
\subsubsection*{Operations Interface}
\subsubsection*{Operation GetCar}


\subsection{Excercise APIPartDMCar}
\subsubsection*{Content of the API Folder}
\subsubsection*{Generated Files}
\subsubsection*{File CarController.go}
\subsubsection*{Mathod GetCar}

\subsection{Excercise InfrastructurePartDMCar}
\subsubsection*{Content of the Infrastructure Folder}
\subsubsection*{Persistence Entities}
\subsubsection*{Mappers}
\subsubsection*{InMemoryRepository}


\subsection{Excercise CSGetCar}
\subsubsection*{Code Sketch GetCar}
\subsubsection*{GetCar Flow Through the Code Sketch}


\subsection{Challenge Operation AddCar}
\subsubsection*{Update API Diagram}
\subsubsection*{Update API Specification}
\subsubsection*{Implement Operation AddCar}
\subsubsection*{Regenerate API Server}
\subsubsection*{Implement Route at API Controller}
\subsubsection*{Complete Repository Implementation}
\subsubsection*{Run Microservice}